cvx-flats

### 2020-04-24 neurips-20/cvx-flats.tex
Fixing statement of Lemma 2

\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the finite property $\gamma$ indirectly elicited by the convex loss $L : \reals^d \times \Y \to \reals$ and distribution $p \in \simplex$.
	The subspace $F := \F_\C(p) \cap (-\F_\C(p))$ is a flat of the loss $L$, contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
\end{lemma}
\begin{proof}
	\jessie{TODO}
\end{proof}

>>>>

\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \F_{\gamma_r}(p) \cap (-\F_{\gamma_r}(p))$ is a flat containing $p$, and $F \cap \simplex \subseteq \gamma_r$.
\end{lemma}
\begin{proof}
	\jessie{TODO}
\end{proof}
